On g~0~

### 2017-03-15 manuscript.Rmd
Added WTC4 figure; manuscript organized a bit with headers; figures inserted; html output option

---
title: "On g~0~"
author: ''
date: ''
output:
  word_document:
    reference_docx: manuscriptstyle.docx
csl: global-change-biology.csl
bibliography: references.bib
---

@@

@@

1. Importance of stomatal conductance. Prevalence of the Ball-Berry model, and g0. What is g0? Point of this paper.

2. Nighttime conductance not necessarily same as minimum conductance

@@

@barbour2007 considerable stomatal control during the night; mirrors daytime

@howard2007 nighttime conductance lower in drought. Nighttime 2-5x higher than cuticular.

We are not reviewing nighttime conductance here, that has been done extensively by others [@caird2007]

2b. Variation in g0

@@

3. How do we estimate g0 from gas exchange?

Poorly, that's how! Problem of correlation between g1 and g0; reason why compilations like Lin et al. set g0 to zero.
Problem that g0 is frequently negative (e.g. @heroult2013)

4. Components of minimum conductance

- Stomata simply do not close all the way, might stay open regardless of photosynthesis, or are broken.

5. Cuticular conductance

- Kerstiens
- H2O not CO2? [@boyer1997]
- gmin as a plastic trait. Temperature response generally unresolved [@kerstiens2006]
- @riederer2001 correlation between temperature and gcut (non-stomatal cuticles)
- @burghardt2003 gmin review
- @schreiber1996 cuticle review

@@

@leuning1995 discusses g0

@@

[@leuning_critical-appraisal_1995]

Various measures of minimum conductance

@@

1. Ball-Berry relation, showing g0 on intercept. Second panel correlation ellipse g0 ~ g1 for one study. Third panel g0 vs. R2 for the Lin dataset.

2. DeKauwe2015 figure A2 redone (minimum photosynthesis, minimum conductance)

3. Kerstiens data: differences between methods, connection to climate data (speciesmap)

4. Blackman data: cuticular conductance is a plastic trait

>>>>

---
title: "On g~0~"
author: ''
date: ''
output:
  html_document:
    theme: flatly
  word_document:
    reference_docx: manuscriptstyle.docx
csl: global-change-biology.csl
bibliography: references.bib
---

@@

```{r echo=FALSE}
includefigs <- TRUE
library(png)
library(grid)

plotfig <- function(...)grid.raster(readPNG(...))
```

@@

Importance of stomatal conductance. Prevalence of the Ball-Berry model, and g0. What is g0? Point of this paper.

# Do we need g~0~ in simulations of water and carbon fluxes?

g~0~ modifies not just conductance in zero light, but also low light and high VPD/ high T. It is commonly observed and makes sense that Ci converges to Ca at zero light, but the coupled leaf gas exchange model does not predict that unless a g0 is included [@leuning1995].

similarly at high T. See also Kala. Figure 1.

@@

# g~0~ is poorly estimated from regression

Barnard and Bauerle said so too but gave no details.
Even in very good datasets, g0 and g1 are strongly correlated (Figure 2).
Across datasets, g0 increases when the model fits poorly (Figure 3), and the width of the confidence interval increases when less variation in a ball-berry coefficient.
Often g0 is even negative [@heroult2013; @leuning1990], so it is often set to some arbitrary value

# Components of g0

## nighttime
Nighttime conductance not necessarily same as minimum conductance
We are not reviewing nighttime conductance here, that has been done extensively by others [@caird2007]

gnight not constant 
@barbour2007 considerable stomatal control during the night; mirrors daytime
@howard2007 nighttime conductance lower in drought. Nighttime 2-5x higher than cuticular.

@@

Stomata simply do not close all the way, might stay open regardless of photosynthesis, or are broken.

## minimum conductance

true cuticular
MLD method (Figure 6) gives higher values but this is probably more useful for models (since these are whole leaves)

@@

conductance: cuticle + closed stomata + cracks, broken stomata

- Kerstiens
@boyer1997 shows that water but not CO~2~ diffuses across non-stomatal cuticles.

@@

- gmin as a plastic trait. Temperature response generally unresolved [@kerstiens2006]
- @riederer2001 correlation between temperature and gcut (non-stomatal cuticles)
- @burghardt2003 gmin review
- @schreiber1996 cuticle review

# Future directions

@@

```{r fig.height=6,echo=FALSE, eval=includefigs}
plotfig("output/figure1.png")
```

**Figure 1**. Simulations with the plantecophys R package, with and without a g~0~. For the bottom two panels, VPD and T~air~ were covaried based on an empirical relationship, reflecting the fact that they covary in field conditions. For all simulations it is assumed that T~leaf~ is equal to T~air~. Parameters were, etc.

```{r fig.height=4,echo=FALSE, eval=includefigs}
plotfig("output/figure2.png")
```

**Figure 2**. Example linear regression of stomatal conductance (g~s~) against a stomatal index, here the linearized version of the model of Medlyn et al. (2011). Example data is taken from Lin et al. (2015), chosen is a dataset with a very good fit as an example. Solid line is regression line, shaded area a 95% confidence interval. Right panel, visualized correlation between estimated slope (g~1~) and intercept (g~0~) of the regression. Dotted ellipse is a bivariate 95% confidence interval (using confidenceEllipse from the car R package), symbols 1000 bootstrap samples of the coefficients (using bootCase in the car R package).

```{r fig.height=4,echo=FALSE, eval=includefigs}
plotfig("output/figure3.png")
```

**Figure 3**.

```{r fig.width=4,echo=FALSE, eval=includefigs}
plotfig("output/figure4.png")
```

**Figure 4**.

```{r fig.height=5, fig.width=5, echo=FALSE, eval=includefigs}
plotfig("output/figure5.png")
```

**Figure 5**.

```{r fig.height=4,echo=FALSE, eval=includefigs}
plotfig("output/figure6.png")
```

**Figure 6**.
